Run the model

### 2019-10-23 scripts/3_model/1_checks.Rmd
Deleted a bunch of old files

# Load functions
source(here("scripts", "model", "E_vec_fxn.R"))
source(here("scripts", "model", "pi_of_E.R"))
source(here("scripts", "model", "max_Ei.R"))

@@

# Load historical effort received and summarize
act <- readRDS(here("raw_data", "activity_by_vessel_year_eez.rds")) %>%
  filter(
    eez_iso3 %in% VDS_countries,
    best_vessel_class == "tuna_purse_seines"
  ) %>%
  group_by(year, eez_iso3) %>%
  summarize(days = sum(hours_length) / 24) %>%
  arrange(desc(days)) %>%
  mutate(
    days_prop = days / (sum(days) / (1 - prop_hs)),
    c_days_prop = cumsum(days_prop)
  )
```

>>>>

# Load functions
source(here("scripts", "3_model", "E_vec_fxn.R"))
source(here("scripts", "3_model", "pi_of_E.R"))
source(here("scripts", "3_model", "max_Ei.R"))

@@

# Load historical effort received and summarize
act <- readRDS(here("raw_data", "activity_by_vessel_year_eez.rds")) %>%
  filter(eez_iso3 %in% VDS_countries) %>%
  group_by(year, eez_iso3) %>%
  summarize(days = sum(hours_length) / 24) %>%
  arrange(desc(days)) %>%
  mutate(days_prop = days / (sum(days)))
```

### 2019-10-23 scripts/3_model/2_run_model.Rmd
Deleted a bunch of old files

# Load functions
source(here("scripts", "model", "grow.R"))
source(here("scripts", "model", "E_vec_fxn.R"))
source(here("scripts", "model", "pi_of_E.R"))
source(here("scripts", "model", "max_Ei.R"))
source(here("scripts", "model", "solve_pi.R"))
source(here("scripts", "model", "PNA_with_trading.R"))
source(here("scripts", "model", "PNA_no_trading.R"))

@@

```{r}
source(here("scripts", "model", "allocate.R"))
source(here("scripts", "model", "allocate_wrap.R"))
source(here("scripts", "model", "move_in_time.R"))
source(here("scripts", "model", "move_in_time_no_trading.R"))
```

>>>>

# Load functions
source(here("scripts", "3_model", "grow.R"))
source(here("scripts", "3_model", "E_vec_fxn.R"))
source(here("scripts", "3_model", "pi_of_E.R"))
source(here("scripts", "3_model", "max_Ei.R"))
source(here("scripts", "3_model", "solve_pi.R"))
source(here("scripts", "3_model", "PNA_with_trading.R"))
source(here("scripts", "3_model", "PNA_no_trading.R"))

@@

```{r}
source(here("scripts", "3_model", "allocate.R"))
source(here("scripts", "3_model", "allocate_wrap.R"))
source(here("scripts", "3_model", "move_in_time.R"))
source(here("scripts", "3_model", "move_in_time_no_trading.R"))
```
